### 2019-07-08 thesis.tex
changes

\chapter{Kinetic theory and astrophysical plasmas}
\label{sec:kin-theo}

The plasma is a collection of ions, electrons and neutral particles that has
its dynamics dominated by the electric and magnetic fields, generated by the
electrically charged particles and the electric currents related to their
motion, respectively. Due to the long-range nature of these self-generated
fields, one particle affects the movement of several other particles, which
will interact with other particles, and so on. This \emph{collective behavior}
\footnote{A detailed exposition of all the processes and conditions that
  characterize the collective behavior in plasmas, can be accessed in the
  following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
is what characterizes an ionized gas as a plasma, and is also the reason
behind the complexity of the plasma dynamics. This complexity comes in the
form of a myriad of self-consistent oscillatory processes, where the electric
and magnetic fields affect - and are affected by - the position and motion of
the charges, and how they vary in time \cite{chen}.

A complete description of such a complicated dynamics would depend on determining
the position and momentum of each particle, and their respective microscopic
electric and magnetic fields, in a given instant in time. This strategy is not
practical and in most of the cases not feasible for many-body systems, like the
plasma. However, this microscopic description can be dealt through a hierarchy of
approximations, leading to the three main theories of plasma physics: kinetic,
multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
formulations will depend on the phenomenon that needs to be described.

\section{Kinetic processes in astrophysical plasmas}
\label{sec:astro-plasma}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{corona2017.png}
    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{fig1}
  \end{center}
\end{figure}

@@

\subsection{Noneigenmode contribution to nonlinear wave
  kinetic equation}
For the nonlinear wave kinetic equation, the implementation
is far more extensive and complicated than the two previous
cases. Such complex series of steps is not well suited to a
Qualifying Exam text but to a PhD Thesis, where they can be
properly explained and then, well comprehended by the reader.
In this text, we provide a brief explanation of the method,
which is not very different from the quasilinear case, though
it is way more complex, and present some important remarks
regarding the inclusion of noneigenmodes in the nonlinear wave
equation. It is worth to mention again that the process of
inclusion of the noneigenmode contribution in the wave and the
particle kinetic equations can be seen in Ref. \cite{YZKS16}.

@@

After an extensive algebraic manipulation that involves making explicit
use of definition \cref{field-fluc} in the noneigenmode field fluctuations,
carrying out the $\omega '$ integrations, then using Eq. \eqref{principal}
to decompose the denominators
$1/\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha-{\bf k'\cdot v})$
and $1/\epsilon^*({\bf k},\omega)$ into principal parts and imaginary terms,
and taking the imaginary part of the resulting equation, we finally obtain
the noneigenmode corrections to the nonlinear wave kinetic equation:
\begin{equation}
  \label{corr}
  \begin{split}
    \mbox{corr}&=-\sum_{\sigma '}\sum_\beta\sum_a \,8\pi e_a^2
    \int d{\bf k'}\int d{\bf v}\,
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^\beta|{\bf k-k'},
      ({\bf k-k'}){\bf \cdot v})|^2}
    {|{\bf k-k'}|^2|\epsilon[{\bf k-k'},{\bf k-k'},({\bf k-k'}){\bf \cdot v}]|^2}\\
    &\times \left[ \frac{I_{\bf k}^{\sigma \alpha}}
      {\epsilon '({\bf k'},\sigma '\omega_{\bf k'}^\beta)}
      -\frac{I_{\bf k'}^{\sigma '\beta}}
	{\epsilon '({\bf k},\sigma \omega_{\bf k}^\alpha)}\right] 
    \delta[\sigma\omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^\beta
    -({\bf k-k'}){\bf \cdot v}]f_a({\bf v})\\
    &-\sum_a \frac{4 e_a^2}{\pi}
    \int d{\bf k '}\int d{\bf v}\,\mbox{Im}\biggl[ \mathcal{P}\,
    \frac{2[\chi^{(2)}({\bf k'},{\bf k' \cdot v}|{\bf k-k'},
      \sigma\omega_{\bf k}^\alpha-{\bf k'\cdot v})]^2}
    {\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha-{\bf k'\cdot v})}\\
    &-\bar \chi^{(3)}({\bf k'},{\bf k' \cdot v}|{\bf -k'},{\bf -k'\cdot v}
    |{\bf k},\sigma\omega_{\bf k}^\alpha)\biggr]
    \frac{I_{\bf k}^{\sigma \alpha}}{k'^2|\epsilon({\bf k'},{\bf k'\cdot v})|^2}
    f_a({\bf v})\\
    &+\sum_a\sum_b \frac{24 e_a^2 e_b^2}{\pi}\int d{\bf k '}
    \int d{\bf v} \int d{\bf v'}\,
    \frac{|\chi^{(2)} \left[ {\bf k'},{\bf k' \cdot v'}|
     {\bf k-k'},({\bf k-k'}){\bf \cdot v} \right]|^2}{k'^2|{\bf k-k'}|^2
   |\epsilon({\bf k'},{\bf k'\cdot v'})|^2
 |\epsilon({\bf k-k'},({\bf k-k'}){\bf \cdot v})|^2}\\
    &\times \frac{\delta \left[ \sigma\omega_{\bf k}^\alpha-{\bf k \cdot v}
	+{\bf k' \cdot}({\bf v-v'})\right]}
    {\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}f_a({\bf v}) f_b({\bf v'}).
  \end{split}
\end{equation}

@@

\chapter{Extra publication}
\label{appC}
This publication is mainly related with the results results presented in
Ref. \cite{Tigik2017a}.
We can say that most of the ideas about the physical processes occurring
in \cite{Tigik2017a}, regarding the formation of the core-halo velocity
distribution and the fact that the electrostatic bremsstrahlung could be
the underlying process behind the ubiquity of such velocity distribution
in the space environment, came from the analysis of the results presented
in \cite{Tigik2017b}.

\includepdf[pages=-]{Tigik2017b.pdf}
\end{appendix}

>>>>

\chapter{Kinetic theory of plasmas}
\label{sec:kin-theo}

% The plasma is a collection of ions, electrons and neutral particles that has
% its dynamics dominated by the electric and magnetic fields, generated by the
% electrically charged particles and the electric currents related to their
% motion, respectively. Due to the long-range nature of these self-generated
% fields, one particle affects the movement of several other particles, which
% will interact with other particles, and so on. This \emph{collective behavior}
% \footnote{A detailed exposition of all the processes and conditions that
%   characterize the collective behavior in plasmas, can be accessed in the
%   following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
% is what characterizes an ionized gas as a plasma, and is also the reason
% behind the complexity of the plasma dynamics. This complexity comes in the
% form of a myriad of self-consistent oscillatory processes, where the electric
% and magnetic fields affect - and are affected by - the position and motion of
% the charges, and how they vary in time \cite{chen}.

% A complete description of such a complicated dynamics would depend on determining
% the position and momentum of each particle, and their respective microscopic
% electric and magnetic fields, in a given instant in time. This strategy is not
% practical and in most of the cases not feasible for many-body systems, like the
% plasma. However, this microscopic description can be dealt through a hierarchy of
% approximations, leading to the three main theories of plasma physics: kinetic,
% multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
% formulations will depend on the phenomenon that needs to be described.

@@

\subsection{Noneigenmode contribution to nonlinear wave kinetic equation}
For the nonlinear wave kinetic equation, the implementation is far more
extensive and complicated than the two previous cases. 
In this text, we provide a brief explanation of the method,
which is not very different from the quasilinear case, though
it is way more complex, and present some important remarks
regarding the inclusion of noneigenmodes in the nonlinear wave
equation. It is worth to mention again that the process of
inclusion of the noneigenmode contribution in the wave and the
particle kinetic equations can be seen in Ref. \cite{YZKS16}.

@@

After an extensive algebraic manipulation that involves making explicit
use of definition \eqref{field-fluc} in the noneigenmode field fluctuations,
carrying out the $\omega '$ integrations, then using Eq. \eqref{principal}
to decompose the denominators
$1/\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha-{\bf k'\cdot v})$
and $1/\epsilon^*({\bf k},\omega)$ into principal parts and imaginary terms,
and taking the imaginary part of the resulting equation, we finally obtain
the noneigenmode corrections to the nonlinear wave kinetic equation:
\begin{equation}
  \label{corr}
  \begin{split}
    \mbox{corr}&=-\sum_{\sigma '}\sum_\beta\sum_a \,8\pi e_a^2
    \int d{\bf k'}\int d{\bf v}\,
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^\beta|{\bf k-k'},
      ({\bf k-k'}){\bf \cdot v})|^2}
    {|{\bf k-k'}|^2|\epsilon[{\bf k-k'},{\bf k-k'},({\bf k-k'}){\bf \cdot v}]|^2}\\
    &\times \left[ \frac{I_{\bf k}^{\sigma \alpha}}
      {\epsilon '({\bf k'},\sigma '\omega_{\bf k'}^\beta)}
      -\frac{I_{\bf k'}^{\sigma '\beta}}
	{\epsilon '({\bf k},\sigma \omega_{\bf k}^\alpha)}\right] 
    \delta[\sigma\omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^\beta
    -({\bf k-k'}){\bf \cdot v}]f_a({\bf v})\\
    &-\sum_a \frac{4 e_a^2}{\pi}
    \int d{\bf k '}\int d{\bf v}\,\mbox{Im}\biggl[ \mathcal{P}\,
    \frac{2[\chi^{(2)}({\bf k'},{\bf k' \cdot v}|{\bf k-k'},
      \sigma\omega_{\bf k}^\alpha-{\bf k'\cdot v})]^2}
    {\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha-{\bf k'\cdot v})}\\
    &-\bar \chi^{(3)}({\bf k'},{\bf k' \cdot v}|{\bf -k'},{\bf -k'\cdot v}
    |{\bf k},\sigma\omega_{\bf k}^\alpha)\biggr]
    \frac{I_{\bf k}^{\sigma \alpha}}{k'^2|\epsilon({\bf k'},{\bf k'\cdot v})|^2}
    f_a({\bf v})\\
    &+\sum_a\sum_b \frac{24 e_a^2 e_b^2}{\pi}\int d{\bf k '}
    \int d{\bf v} \int d{\bf v'}\,
    \frac{|\chi^{(2)} \left[ {\bf k'},{\bf k' \cdot v'}|
     {\bf k-k'},({\bf k-k'}){\bf \cdot v} \right]|^2}{k'^2|{\bf k-k'}|^2
   |\epsilon({\bf k'},{\bf k'\cdot v'})|^2
 |\epsilon({\bf k-k'},({\bf k-k'}){\bf \cdot v})|^2}\\
    &\times \frac{\delta \left[ \sigma\omega_{\bf k}^\alpha-{\bf k \cdot v}
	+{\bf k' \cdot}({\bf v-v'})\right]}
    {\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}f_a({\bf v}) f_b({\bf v'}).
  \end{split}
\end{equation}

@@

\chapter{Extra publication}
\label{appC}
This publication is mainly related with the results presented in
Ref. \cite{Tigik2017a}.
We can say that most of the ideas about the physical processes occurring
in \cite{Tigik2017a}, regarding the formation of the core-halo velocity
distribution and the fact that the electrostatic bremsstrahlung could be
the underlying process behind the ubiquity of such velocity distribution
in the space environment, came from the analysis of the results presented
in \cite{Tigik2017b}.

\includepdf[pages=-]{Tigik2017b.pdf}

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and technically infinite energy source
when scientists and engineers manage to succeed at obtaining a controlled, and
energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
everyday life are rare, restricted to the occurrence of lightning during storms,
flames, and the beautiful auroras that take place at high latitudes. In the
interplanetary and interstellar space, however, the situation is the opposite.
Starting in the outer layers of Earth's atmosphere, passing through the solar
wind in the interplanetary space, to the stellar interiors and atmospheres,
accretion disks, and molecular clouds it is estimated that something around
$99 \sim 99.9\%$ of the observable matter is in the plasma state \cite{may}. 
Therefore, the study and comprehension of the physics of plasma processes is a
fundamental branch of astrophysics.

The

% \section{Kinetic processes in astrophysical plasmas}
% \label{sec:astro-plasma}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{corona2017.png}
    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{figD1}
  \end{center}
\end{figure}

\end{appendix}
